E1: ENRON Sentiment

### 2016-03-25 paper/paper.tex
up

In the past years, several email datasets from diverse sources have been publicly released.
In this paper, we analyse the famous ``ENRON Corpus'' which contains 620k messages in about 150 mailboxes belonging to ENRON employees involved in a court case.
We extract and analyse sentiments within those messages using functional programming together with a well known engine for large-scale data processing. 
Thus, the analysis is run in a high performance computing cluster.   
We present our result as an interactive visualisation of the sentiment spread via emails together with the company's stock price of the same period.
\hlc{TODO: aggiungere le conclusioni!!!!!!!!!!!}

@@

Our outcome is a visualisation of the sentiment extracted from employees' emails together with the ENRON's stock price of the same period.
\hlc{TODO: aggiungere le conclusioni!!!!!!!!!!!}

@@

\section{Conclusions}
\label{sec:concl}
In this section we present some conclusions based on our results, considering the research questions listed in Section~\ref{sec:r-q}.
Although, our results include a visualisation of sentiment information contained within the ``ENRON Corpus''.
Therefore, we claim the sentiment extraction from an emails dataset is actually doable. 
However, we highlight that in order to simplify our task we made some assumptions.
On one hand, we claim this is absolutely common, and sometimes even necessary, in a large-scale data processing.
On the other hand, the number and kind of assumptions might not be negligible.
For instance, we have chosen to take into account only those recipients which appears to have a personal mailbox in our dataset.
Therefore, people from outside the company and other employes are simply ignored.
Given that those people have most likely contributed to the sentiment coded in the emails, we argue this assumption is rather strict and further investigations should assess weather it is the case.  
\hlc{Furthermore, we claim that our visualisation provides useful hints for highlighting a not so strong correlation between emails' sentiment and the ENRON's stock price.
We argue this fact might be due to noise in our dataset,
Moreover, further experiments should be run with different settings, for example we could try different sentiment extraction techniques and other overall sentiment scoring functions.}
Lastly, we observe the research question about the influence of individual behaviours cannot find answer in this work.
This is mainly due to the lack of time to run further experiments.

>>>>

In the past years, several email datasets from diverse sources have been publicly released.
In this paper, we analyse the famous ``ENRON Corpus'' which contains 620k messages in about 150 mailboxes belonging to ENRON employees involved in a court case.
We extract and analyse sentiments within those messages using functional programming together with a well known engine for large-scale data processing. 
Thus, the analysis is run in a high performance computing cluster.   
We present our result as an interactive visualisation of the sentiment spread via emails together with the company's stock price of the same period.
Our results show there is a weak correlation between the company's stock price and the sentiments extracted from the email corpus.

@@

Our outcome is a visualisation of the sentiment extracted from employees' emails together with the ENRON's stock price of the same period.
Our experiment shows there is just a weak correlation between ENRON's stock price drop and sentiments extracted from the company's email dataset.

@@

\section{Conclusions}
\label{sec:concl}
In this section we present some conclusions based on our results, considering the research questions listed in Section~\ref{sec:r-q}.
Although, our results include a visualisation of sentiment information contained within the ``ENRON Corpus''.
Therefore, we claim the sentiment extraction from an emails dataset is actually doable. 
However, we highlight that in order to simplify our task we made some assumptions.
On one hand, we claim this is absolutely common, and sometimes even necessary, in a large-scale data processing.
On the other hand, the number and kind of assumptions might not be negligible.
For instance, we have chosen to take into account only those recipients which appears to have a personal mailbox in our dataset.
Therefore, people from outside the company and other employes are simply ignored.
Given that those people have most likely contributed to the sentiment coded in the emails, we argue this assumption is rather strict and further investigations should assess weather it is the case.  
Furthermore, we claim that our visualisation provides useful hints for highlighting a not so strong correlation between emails' sentiment and the ENRON's stock price.
We argue this fact might be due to noise in our dataset.
Moreover, further experiments should be run with different settings, for example we could try different sentiment extraction techniques and other overall sentiment scoring functions.
Lastly, we observe the research question about the influence of individual behaviours cannot find answer in this work.
This is mainly due to the lack of time to run further experiments.
